Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-02-07 Writing/manuscript_cea.rmd
further modifications to the manuscript and replies

Virtually all the previous studies have used yield prediction accuracy to rank and select models. This is understandable, since whereas yield can be "ground-truthed" the true causal impact of a treatment cannot be determined from real-world data, making it impossible to cross-validate EONR. 
However, the simulation results reported here show clearly that using a model's yield prediction accuracy as a model selection criterion is not well justified if the ultimate objective is accurate estimation of site-specific EONRs.

>>>>

Virtually all the previous studies have used yield prediction accuracy to rank and select models. This is understandable, since whereas yield can be "ground-truthed" the true causal impact of a treatment cannot be determined from real-world data, making it impossible to cross-validate EONR prediction. 
However, the simulation results reported here show clearly that using a model's yield prediction accuracy as a model selection criterion is not well justified if the ultimate objective is accurate estimation of site-specific EONRs.
